A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-08-09 sections/04-research-design.tex
Add text for the abstract, introduction and conclusion.
Reviewing Research Design

This section describes our research design. We devised a questionnaire
regarding student experience with solving the same problem using
\textit{Pthreads} and \textit{OpenMP} during the Concurrent, Parallel and
Distributed Computing Course at the Computer Science program of the University
of São Paulo. We answered 3 research questions using analyses of the students'
responses.

@@

The assignment required that the students measure the performance of the
sequential code and the performance improvements they achieved using
\textit{Pthreads} and \textit{OpenMP}.  After completing the assignment the
students were asked to answer a questionnaire.

@@

The questions of the second part were related to the students'
experience with \textit{Pthreads} and \textit{OpenMP} \textit{after}
the completion of the assignment.

We obtained responses, and consent to use them in our research, from 38 of the
54 students enrolled in the Concurrent, Parallel and Distributed Computing
course. Section \ref{sec:background} presents a detailed description of
each set of questions our analysis of the students' responses.

\subsection{Research Questions}

>>>>

We devised a questionnaire regarding student experience with solving the same
problem using \textit{Pthreads} and \textit{OpenMP} during the Concurrent,
Parallel and Distributed Computing Course at the Computer Science program of
the University of São Paulo. We answered 3 research questions using analyses of
the students' responses.

@@

The assignment required that the students measure the performance of the
sequential code and the performance improvements they achieved using
\textit{Pthreads} and \textit{OpenMP}. After completing the assignment we asked
the students to answer a questionnaire.

@@

The questions of the second part were related to the students'
experience with \textit{Pthreads} and \textit{OpenMP} after
the completion of the assignment.

We obtained responses, and consent to use them in our research, from 38 of the
54 students enrolled in the Concurrent, Parallel and Distributed Computing
course. Section \ref{sec:responses} presents a detailed description of each set
of questions our analysis of the students' responses.

\subsection{Research Questions}
\label{sec:resques}
